Inference methods comparison for the simplified Naomi model

### 2023-05-02 src/naomi-simple_ks/ks.Rmd
Remove MMD and PSIS boilerplate from KS report
Fix #30

```{r}
histogram_and_ecdf(par = "alpha_t1_out", i = 1)
```

@@

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_lambda_t1_out %>% filter(!(age_group %in% c("Y005_009", "Y010_014", "Y080_999"))), par = "lambda_t1_out", alpha = 0.2)
```

What is going on with those very high values of KS?

```{r}
ks_lambda_t1_out %>%
  filter(ks > 0.99) %>%
  group_by(method) %>%
  summarise(n = n())

ks_lambda_t1_out %>%
  filter(ks > 0.99) %>%
  pull(age_group) %>%
  unique()
```

@@

# MMD

```{r}
#' To write!
```

# PSIS

Suppose we have two sets of samples from the posterior.
For each sample we are going to want to evaluate the log-likelihood, so that we can calculate the log-likelihood ratios.
We can extract the `TMB` objective function for the log-likelihood as follows:

```{r}
tmb$fit$obj$fn()
#' To write!
```

>>>>

```{r}
histogram_and_ecdf(par = "rho_t1_out", i = 1)
```

@@

ks_plot(ks_df = ks_rho_t1_out, par = "rho_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_alpha_t1_out, par = "alpha_t1_out", alpha = 0.2)
ks_plot(ks_df = ks_lambda_t1_out, par = "lambda_t1_out", alpha = 0.2)
```

What is going on with those very low values of KS?
It's that there are new new infections in those age groups, and the posterior samples from each method are exactly the same, in particular draws of only zero.

```{r}
ks_lambda_t1_out %>%
  filter(ks == 0) %>%
  group_by(method) %>%
  summarise(n = n())

ks_lambda_t1_out %>%
  filter(ks == 0) %>%
  pull(age_group) %>%
  unique()
```

@@
